### 2015-05-23 docs/report/code_sharing.tex
Added link to context section from code sharing

\section{Code sharing}
The library must handle the distribution of the code between the different workers when an operation is executed. This is a challenging problem with many possible alternatives: Cloud Haskell \cite{cloud-haskell} for example, requires a customized version of the Glasgow Haskell Compiler (GHC) to serialize closures and their captured variables as a code pointer and an environment, operating under the assumption that the same code is executed in all nodes. A proposal for using Scheme for distributed programming \cite{distributed-scheme} uses a custom serializable data structure to represent procedures, and macros in order to capture a closure's captured variables and serialize their values. It also assumes that all nodes are executing the same program since serialized functions store pointers to parts of source code files.

@@

\note{An approach to provide contextual data to worker functions is explored in \todo{link to section}.}

>>>>

\section{Code sharing}\label{sec:code-sharing}
The library must handle the distribution of the code between the different workers when an operation is executed. This is a challenging problem with many possible alternatives: Cloud Haskell \cite{cloud-haskell} for example, requires a customized version of the Glasgow Haskell Compiler (GHC) to serialize closures and their captured variables as a code pointer and an environment, operating under the assumption that the same code is executed in all nodes. A proposal for using Scheme for distributed programming \cite{distributed-scheme} uses a custom serializable data structure to represent procedures, and macros in order to capture a closure's captured variables and serialize their values. It also assumes that all nodes are executing the same program since serialized functions store pointers to parts of source code files.

@@

\note{An approach to provide contextual data to worker functions is explored in Section~\ref{sec:context}.}
